---
title: "HW3 MVS"
author: "Sanjay Chhetri"
date: "11/8/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Part A: Logistic Regression
 
Instruction: "For the logistic regression analysis, you will be employing a list-wise deletion approach to handling missing data (which is also what logistic regression does by default). You will be using the following five variables in your analysis: Sex, Marital, Health, Unhappy, and Depression".

```{r loading, include = TRUE}
library(haven)
df <- read_sav("GSS2018_HW3A.sav")
head(df, 10)
```

### Q.N. 1
How many participants have complete data on these five variables? What percentage is this of the full sample? 

```{r Q.N. 1}
nrow(df)
sum(complete.cases(df))
df$complete_case <- complete.cases(df)
708/2348*100

```
Out of total 2348 observations in the datafile, 708 are complete cases. It is `r 708/2348*100` percent of the full sample. 

### Q.N. 2
```{r Chi-Square Tests}
test_sex <- chisq.test(table(df$Sex, df$complete_case)) 
test_sex
test_marital <- chisq.test(table(df$Marital, df$complete_case))
test_marital
test_Health <- chisq.test(table(df$Health, df$complete_case))
test_Health
test_unhappy <- chisq.test(table(df$Unhappy, df$Depression))
test_unhappy
test_depression <- chisq.test(table(df$Depression, df$complete_case))
test_depression
```
Sex, Marital, Health, and Depression variables each do not seem to predict the distribution of missingness in the dataset. But Unhappy variable seems to predict the distribution of missingness in the dataset. 

### Q.N.3
```{r complete case subset, include=TRUE}
dfc <- df %>% filter(complete_case)
head(dfc, 10)
nrow(dfc)
summary(dfc)
par(mfrow = c(2,2))
hist(dfc$Sex)
hist(dfc$Marital)
hist(dfc$Unhappy)
hist(dfc$Depression)
```

## Q.N. 4
```{r logistic regression, include = T}
dfc$Sex <- factor(dfc$Sex)
dfc$Marital <- factor(dfc$Marital)
logistic_model <- glm(Depression~Sex+Marital+Health+Unhappy, data = dfc, family = "binomial")
summary(logistic_model)
exp(cbind(OR = coef(logistic_model), confint.default(logistic_model)))
```

According to the results, sex, health, Martial and unhappy significantly predict odds of depression. 
Sex was significantly associated with the odds of depression. Specifically, females have 2.93 times the odds of having depression than males (95% CI: [1.89, 4.54])
Marital status was also significantly predicted the odds of depression. Specifically, unmarried people have 1.6 times the odds of being depressed than married people (95% CI: [1.03, 2.42]
Health is also significantly associated with the odds of depression. For each unit worsening of health, the odds of getting depression goes up by 1.5 (95% CI: [1.21, 1.81]).
State of unhappiness also predicts depression. Specifically, each unit decrease in happiness level is associated with 1.71 odds of getting depression(95% CI:[1.21, 2.41 ]

#Part C


``` {r interaction check}
survey <- read_sav("survey.sav")
head(survey)
int <- aov(Mslfest~age_group*Mlifesat, data = survey)
summary(int)

```

The interaction terms is significant. 

```{r titanic}
titanic <- read_csv("titanic.csv")
head(titanic)
table(titanic$Survived)
titanic %>% ggplot(aes(Survived))+ geom_bar()
```
Out of total 887 people, 545 people died and only 342 survived. 

``` {r glm on titanic}
survival <- glm(Survived~factor(Pclass)+factor(Sex)+Age, data = titanic)
summary(survival)
exp(cbind(OR = coef(survival), confint.default(survival)))

```

All predictors in the model had individual main effects on survival status. 
Passenger class (Pclass) significantly predicted survival. Specifically, compared to the first class passengers, the second class passengers had about 20% less odds of survival and the third class passengers had about 32% less odds of survival (all else being equal). 
Sex also predicted survival. Specifically, males had 40% less odds of survival than females. 
Age also predicted survival. Each year increase of age predicted 1% decrease in survival odds. 






















